Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory

### 2016-08-05 letters/reply_referee.tex

Our paper has been reviewed by two of your Referees,
who recommended it for the publication in the
New Journal of Physics subject to minor amendments.
We are thankful for the comments made by the Referees and
respond to them below.

\textbf{Referee \#1} raised the following points:

\begin{enumerate}
 \item \emph{In general, I find the manuscript clearly written but unnecessary long. Some details and discussions can be avoided without weakening the presentation. Here are some examples:}
  \begin{enumerate}
   \item \emph{ICD is explained twice in the introduction (top of page 3 and
         3rd paragraph of page 3)}\\

				We have deleted the explanation of ICD in the 3rd paragraph of page 3.

@@

   \item \emph{Page 10: the definition of open and close channel is repeated. Explanations in page 9 and figure 1 are enough.}\vspace{0.3cm}\\
         The explanation on page 10 belongs to the explanation on page 9, which
         would not be understandable without half of the text. While the
         text formulates the general concept, the figure illustrates this concept
         on an example which is this manuscript's system under investigation.
         Since also the caption of the figure should be understandable without
         reading the text, we do not shorten the manuscript at this point.

   \item \emph{Page 13:
         the section “Cluster Structures” can be moved to Supporting information since only Table 2 is important to understand the results. Furthermore, it seems to me that the paragraph on previous study of the authors on large clusters does provide relevant informations on the reported results.}\vspace{0.3cm}\\
         We object to move the pictures showing
         some classes of systems under investigation,
         which is far less the all systems, to the
         supplementary information. Additionally, the paragraph the reviewer
         refers to are two paragraphs. Since the section only consists of
         four paragraphs in total, the first one explains the general
         procedure of the manuscript and the fourth explains the pictures of
         the classes, there is nothing left to reasonably be moved to the
         Supplementary Information. We therefore don't change the manuscript
         in this point.

   \item \emph{Page:
         the section Outer valence spectra is very detailed and the reader may lose the main point of this section which is, as far as I understood, to evaluate experimentally the percentage of Xe in the clusters. All extra details can be avoided. Just to help the readers, this section could be renamed to highlight the goal of the section like for example “Xe content”.}

				The referee is correct if one reads the article from a theoreticians point of view. However, the outer valence spectra of our clusters were not reported in this detail earlier nor were they ever discussed. We therefore think that this section holds very valuable information for the experimentalist which we do not want to hide in the supplementary section. To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: {\color{blue}{This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters. The main information we obtain from these spectra within the context of our theoretical considerations are
the single ionization potentials and
the relative Xe contents in the mixed cluster.}}

@@

 \item \emph{Page 12:
       On page 12 last line there is to Tables II and III. I have not been able to locate these. The reference should be clarified.}\\
       The sentence has been changed to:\\
       In this work we evaluate the secondary energies and decay widths with
       the programme HARDRoC$^{20,49}$ using the experimental ionization energies
       of Table 3 and data from the literature given in Tables II and III
       {\color{blue}{of Ref. 34.}}\\
       The following sentence was removed.

 \item \emph{Page 20,21:
       it is not clear what structure of the larger clusters with 3871 atoms is used in the simulation. The authors mention icosahedral and cuboctahedral but no further details are given, e.g. Ar-Xe distance, Ar-Ar distance, etc.}\\
       The details were added to the Cluster Structures section. The last
       sentences now read:\\
       Furthermore, for comparison with the largest measured ArXe clusters,
       we constructed also larger core-shell structures (Table 2, \#4 – 5).
       {\color{blue}{These were idealized icosahedral and cuboctahedral
       structures based on the v. d. Waals radii of argon and xenon
       $r_{Ar} =$\unit[1.88]{\AA}$^{54}$
       and $r_{Xe} =$\unit[2.16]{\AA}$^{55}$.}}

 \item \emph{In fig. 9(a) it is specified in the text that  Ar $<N>$ =190 for the black trace but as far as I can tell no value is given for the other spectrum on the same graph.}

@@

	We have clarified the information in the figure caption and additionally refer to the respective table.

 \item \emph{It is not clear what the dotted lines in Figure 10 are?}

 We have clarified the information in the figure caption by including the sentence: {\color{blue}{The dotted line shows the unscaled spectrum in this region.}}

 \item \emph{The colour schemes of some of the figures lead to confusion when printed in grayscale. Some effort could be made to resolve this.}\vspace{0.3cm}\\
       The reviewer does not specify which figures are affected by this.
       We therefore assume a reference to figures 4-8. In these, the
       information density is very high, especially within the stick spectrum.
       Due to this, overlapping dotted or dashed lines would not be
       decipherable and only confuse the reader not only on a grayscale print
       but also a coloured print. Since the majority of scientific journals
       at least have the pdf version available as well, we therefore leave
       the colour choice, which was made to allow readability by
       colour blind people as well.

### 2016-08-05 exp_results.tex
correct smaller errors

\subsection{Outer valence spectra}
%
This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters. The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed clusters (see Table\ \ref{tab:valence}). 
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
(a) shows the outer valence region of homogeneous Ar(1) (red) Ar(2) (black) and Xe clusters, respectively (see text and Table\ \ref{tab:cluster} for details). 
The two lower panels show spectra of the mixed species with different mean size. 
Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
% verschiedene CLustergrößen?}}
}
 \label{figure:oval1}
\end{figure}

>>>>

\subsection{Outer valence spectra}
%
This section describes and discusses the outer valence spectra of the mixed
Ar-Xe clusters. The main information we obtain from these spectra within
the context of our theoretical considerations are the single ionization
potentials and the relative Xe
contents in the mixed clusters (see Table\ \ref{tab:valence}). 
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
(a) shows the outer valence region of homogeneous Ar(1) (red) Ar(2) (black) and Xe clusters, respectively (see text and Table\ \ref{tab:cluster} for details). 
The two lower panels show spectra of the mixed species with different mean size. 
Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
% verschiedene CLustergrößen?}}
}
 \label{figure:oval1}
\end{figure}
